
\begin{thebibliography}{9}
  
\bibitem{laskowski}
  Michael C. Laskowski, \textit{A simpler axiomatization of the Shelah-Spencer almost sure theories},
  Israel J. Math. \textbf{161} (2007), 157–186. MR MR2350161	
\bibitem{density}
  M. Aschenbrenner, A. Dolich, D. Haskell, D. Macpherson, S. Starchenko,
  \textit{Vapnik-Chervonenkis density in some theories without the independence property}, I,
  Trans. Amer. Math. Soc. 368 (2016), 5889-5949
\bibitem{reduct}
  E. Leenknegt. \textit{Reducts of $p$-adically closed fields}, Archive for Mathematical Logic, 53(3):285-306, 2014
\bibitem{ash7} 
  P. Assouad, \textit{Densit´e et dimension}, Ann. Inst. Fourier (Grenoble) 33 (1983), no. 3, 233–282.
\bibitem{ash8}
  P. Assouad, \textit{Observations sur les classes de Vapnik-Cervonenkis et la dimension combinatoire de Blei},
  in: Seminaire d’Analyse Harmonique, 1983–1984, pp. 92–112, Publications Math´ematiques
  d’Orsay, vol. 85-2, Universit´e de Paris-Sud, D´epartement de Math´ematiques, Orsay, 1985.
\bibitem{sauer}
  N. Sauer, \textit{On the density of families of sets}, J. Combinatorial Theory Ser. A 13 (1972), 145–147.
\bibitem{shelah}
  S. Shelah, \textit{A combinatorial problem; stability and order for models and theories in infinitary languages},
  Pacific J. Math. 41 (1972), 247–261.
\bibitem{simon_dp_min}
  P. Simon,
  \textit{On dp-minimal ordered structures},
  J. Symbolic Logic 76 (2011), no. 2, 448-460
\bibitem{parigot_trees}
  Michel Parigot.
  Th\'eories d'arbres.
  \textit{Journal of Symbolic Logic}, 47, 1982, 841-853
\bibitem{stable_graphs}
	Klaus-Peter Podewski and Martin Ziegler. Stable graphs. \textit{Fund. Math.}, 100:101-107, 1978.
\bibitem{infinite_megner}
	Aharoni, Ron and Berger, Eli (2009). "Menger's Theorem for infinite graphs". \textit{Inventiones Mathematicae} 176: 1–62

\bibitem{regularity}
Artem Chernikov, Sergei Starchenko, \textit{Regularity lemma for distal structures}, 	arXiv:1507.01482

\bibitem{value}
Joseph Flenner. \textit{Relative decidability and definability in Henselian valued fields.} The
Journal of Symbolic Logic, 76(04):1240 1260, 2011.
	
\bibitem{nowhere}
J. Nesetril and P. Ossona de Mendez. \textit{On nowhere dense graphs.} European Journal of
Combinatorics, 32(4):600 617, 2011

\bibitem{shelah_dp}
  S. Shelah, \textit{Strongly dependent theories} (2009), preprint.
\bibitem{spencer}
  S. Shelah and J. Spencer, \textit{Zero-one laws for sparse random graphs}, Journal
of AMS 1 (1988) 97-115.  
\bibitem{guingona}
  V. Guingona, C. Hill, \textit{Local dp-rank and VC-density over indiscernible sequences},
  Math. Log. Quart., 60: 59-65
\bibitem{dp_add} 
  I. Kaplan, A. Onshuus, and A. Usvyatsov, \textit{Additivity of the dp-rank},
  Trans. Amer. Math. Soc. 365 (2013), 5783-5804

\end{thebibliography}

\end{document}