\chapter{Inroduction and Preliminaries}

\section{Inroduction}

My research concentrates on the concept of VC-density, a recent notion of rank in NIP theories.
The study of a structure in model theory usually starts with quantifier elimination, followed by a finer analysis of definable functions and interpretability.
The study of VC-density goes one step further, looking at a structure of the asymptotic growth of finite definable families.
In the most geometric examples, VC-density coincides with the natural notion of dimension.
However, no geometric structure is required for the definition of VC-density, thus we can get some notion of geometric dimension for families of sets given without any geometric context.

In 2013, Aschenbrenner et al. investigated and developed a notion of VC-density for NIP structures, an analog of geometric dimension in an abstract setting \cite{density}. Their applications included a bound for $p$-adic numbers, an object of great interest and a very active area of research in mathematics. My research concentrates on improving and expanding techniques of that paper to improve the known bounds as well as computing VC-density for other NIP structures of interest. I am able to obtain new bounds for the additive reduct of $p$-adic numbers, trees, and certain families of graphs. Recent research by Chernikov and Starchenko in 2015 \cite{regularity} suggests that having good bounds on VC-density in $p$-adic numbers opens a path for applications to incidence combinatorics (e.g. Szemeredi-Trotter theorem).

The concept of VC-dimension was first introduced in 1971 by Vapnik and Chervonenkis for set systems in a probabilistic setting \cite{vc71}.
The theory grew rapidly and found wide use in geometric combinatorics, computational learning theory, and machine learning.
Around the same time Shelah was developing the notion of NIP ("not having the independence property"),
a natural tameness property of (complete theories of) structures in model theory \cite{shelah_nip}.
In 1992 Laskowski noticed the connection between the two: theories where all uniformly definable families of sets have finite VC-dimension are exactly NIP theories \cite{laskowski92}.
It is a wide class of theories including algebraically closed fields, differentially closed fields, modules, free groups, o-minimal structures, and ordered abelian groups.
A variety of valued fields fall into this category as well, including the $p$-adic numbers.

The $p$-adic numbers were first introduced by Hensel in 1897 in \cite{hensel}, and over the following century a powerful theory was developed around them with numerous applications across a variety of disciplines, primarily in number theory, but also in physics and computer science.
In 1965 Ax, Kochen \cite{ak1} and Ershov \cite{er1} axiomatized the theory of $p$-adic numbers and proved a quantifier elimination result.
A key insight was to connect properties of the value group and residue field to the properties of the valued field itself.
In 1984 Denef proved a cell decomposition result for more general valued fields \cite{den84}.
This result was soon generalized to $p$-adic subanalytic and rigid analytic extensions, allowing for the later development of a more powerful technique of motivic integration.
The conjunction of those model theoretic results allowed to solve a number of outstanding open problems in number theory (e.g., Artin's Conjecture on $p$-adic homogeneous forms).

In 1997, Karpinski and Macintyre computed VC-density bounds for o-minimal structures and asked about similar bounds for $p$-adic numbers \cite{karp97}.
VC-density is a concept closely related to VC-dimension.
It comes up naturally in combinatorics with relation to packings, Hamming metric, entropic dimension and discrepancy.
 VC-density is also the decisive parameter in the Epsilon-Approximation Theorem, which is one of the crucial tools for applying VC theory in computational geometry.
In a model theoretic setting it is computed for families of uniformly definable sets.
 In 2013, Aschenbrenner, Dolich, Haskell, Macpherson, and Starchenko computed a bound for VC-density in $p$-adic numbers and a number of other NIP structures \cite{density}.
They observed connections to dp-rank and dp-minimality, notions first introduced by Shelah.
In well behaved NIP structures families of uniformly definable sets tend to have VC-density bounded by a multiple of their dimension, a simple linear behavior.
In a lot of cases including $p$-adic numbers this bound is not known to be optimal.
My research concentrates on improving those bounds and adapting those techniques to compute VC-density in other common NIP structures of interest to mathematicians.

Some of the other well behaved NIP structures are Shelah-Spencer graphs and flat graphs.
Shelah-Spencer graphs are limit structures for random graphs arising naturally in a combinatorial context.
Their model theory was studied by Baldwin, Shi, and Shelah in 1997 \cite{shi}, \cite{baldwin}.
Later work of Laskowski in 2006 \cite{laskowski} has provided a quantifier simplification result.
 Flat graphs were first studied by Podewski-Ziegler in 1978, showing that those are stable \cite{stable_graphs}, and later results gave a criterion for super stability.
Flat graphs also come up naturally in combinatorics in work of Nesetril and Ossona de Mendez \cite{nowhere}.
%Shelah-Spencer graphs and flat graphs are both subclasses of NIP theories, extremely well behaved model theoretically.

The first chapter of my dissertation introduces some basics of model theory and defines VC-density and VC-dimension.

The second chapter concentrates on trees.
I answer an open question from \cite{density}, computing VC-density for trees viewed as a partial order.
The main idea is to adapt a technique of Parigot \cite{parigot_trees} to partition trees into weakly interacting parts, with simple bounds of VC-density on each.

In the third chapter of my dissertation I work with Shelah-Spencer graphs.
I have shown that they have infinite dp-rank, so they are poorly behaved as NIP structures.
I have also shown that one can obtain arbitrarily high VC-density when looking at uniformly definable families in a fixed dimension.
However I'm able to bound VC-density of individual formulas in terms of edge density of the graphs they define.

The fourth chapter deals with $p$-adic numbers.
I have shown that VC-density is linear for an additive reduct of $p$-adic numbers
using a cell decomposition result from the work of Leenknegt in 2013 \cite{reduct}.
% I will explore other reducts described in that paper, to see if my techniques apply to those as well.

In chapter five I investigate flat graphs using the work of
Podewski-Ziegler \cite {stable_graphs}.
I am able to show that flat graphs are dp-minimal, an important first step before establishing bounds on VC-density.

\section{Basic Model Theory}

This section goes through the basics of the model theory used throughout this text.
It is meant to be used mostly as a reference on the notation as opposed to a comprehensive summary.
For a complete and more thorough introduction to the material, we refer the reader to Chapters 1 and 2 of \cite{tent}.
We begin with a short summary of languages, formulas, and structures:

\begin{Definition} \ 
  \begin{itemize}
  \item A \defn{language} is a collection of predicate, function, and constant symbols.
  \item Fix a language $\LL$ and a collection of variables.
    A \defn{term} is an expression constructed out of constants, variables, and functions.
  \item An \defn{atomic formula} is an expression constructed out of the equality symbol or a predicate applied to terms.
  \item A \defn{(first-order) formula} is an expression constructed out of atomic formulas using boolean connectives
    $\wedge, \vee, \neg$ and quantifiers $\exists, \forall$.
    We denote such a formula as $\phi(x)$ where $x$ is a tuple of \defn{free variables},
    that is the variables used in $\phi$ that are not bound by quantifiers.
    Abusing notation, we denote $\LL$ to be the set of all such formulas (so we have $\phi \in \LL$).
  \item A formula without free variables is called a \defn{sentence}.
  \item A \defn{quantifier-free} formula is a formula that doesn't contain any quantifiers.
  \item A \defn{structure} $\MM$ consists of an infinite universe $M$ and functions, predicates, and constants matching those of $\LL$.
  \item For a variable tuple $x$, let $|x|$ be the arity of the tuple.
    Similarly, for a tuple $a \in M^n$ let $|a|=n$.
  \item Suppose we have a formula $\phi(x)$, structure $\MM$, and $a \in M^{|x|}$.
    Then we say that $\MM$ \defn{models} $\phi(a)$, denoted as $\MM \models \phi(a)$,
    if the formula $\phi$ holds $\MM$ when we plug in $a$ into $x$.
  \item Suppose we have a structure $\MM$ and $A \subseteq M$.
    Then $\LL(A)$ denotes an expansion of $\LL$ by constant symbols correspoding to elements in $A$.
    The structure $\MM$ then can be viewed as a $\LL(A)$-structure with the appropriate interpretations.
    Formulas $\phi \in \LL(A)$ will be referred to as \defn{formulas with parameters from $A$} or simply as \defn{$A$-formulas}.
    In this context $A$ is usually referred to as a \defn{parameter set}.
  \item A \defn{theory} is a collection of sentences.
  \item For a theory $T$ and a structure $\MM$, we say that $\MM$ \defn{models} $T$,
    or that $\MM$ is a \defn{model} of $T$, if $\MM$ models every sentence in $T$.
  \item For a structure $\MM$, a \defn{theory of $\MM$} is a collection of all sentences that are modelled by $\MM$.
  \item A theory is called \defn{complete} if it is a theory of some structure $\MM$.
  \end{itemize}  
\end{Definition}

Throughout this text we often confuse complete theories with their models.
This is justfied for properties that can be described by a collection of first-order sentences.
Then a theory has this property if and only any (all) models have this property.
An example of that is a notion of stability.

Stability is a deep subject, with a lot of theory developed around it.
We won't work with it directly, but it is a property of some of the structures we study.
We present a definitnon for completeness and refer the reader to Chapter 8 of \cite{tent} or to \cite{pillay} for a more complete introduction.

\begin{Definition} \ 
  \begin{itemize}
  \item Suppose we have a structure $\MM$.
    The formula $\phi(x,y)$ is called \defn{unstable} if for all natural $n$
    there exist $a_i \in M^{|x|}, b_i \in M^{|y|}$ for $0 \leq i \leq n$ such that
    \begin{align*}
      \MM \models \phi(a_i, b_j) \iff i \leq j.
    \end{align*}
  \item A formula is \defn{stable} if it is not unstable.
  \item A structure $\MM$ is \defn{stable} if all of its formulas are stable.
  \item A complete theory $T$ is \defn{stable} if any (all) of its models are stable.
  \end{itemize}
\end{Definition}

Definable sets are subsets of our structure given by formulas.
More precisely:
\begin{Definition}
  Suppose we have a structure $\MM$, a paramter set $A \subseteq M$ and an $A$-formula $\phi(x)$.
  Then 
  \begin{align*}
    \phi(M^{|x|}) = \curly{m \in M^{|x|} \mid \MM \models \phi(m)}
  \end{align*}
  is referred to as an \defn{$A$-definable} subset of $M^{|x|}$ defined by $\phi$.
\end{Definition}

More generally, we will need a slightly more refined notion of a trace:
\begin{Definition}
  Suppose we have a structure $\MM$, a formula $\phi(x, y)$, tuples $a \in M^{|x|}, b \in M^{|y|}$, and
  sets $A \subseteq M^{|x|}, B \subseteq M^{|y|}$. 
  Define
  \begin{align*}
    \phi(A, b) &= \curly{a \in A \mid \MM \models \phi(a,b)}, \\
    \phi(a, B) &= \curly{b \in B \mid \MM \models \phi(a,b)}.
  \end{align*}
  These sets will be informally referred to as traces.
  Similarly, let
  \begin{align*}
    \phi(A, B) = \curly{\phi(A, b) \mid b \in B} \in \PP(A)
  \end{align*}
  denote a collection of traces.
\end{Definition}

Types is one of the main tools of study in model theory.
\begin{Definition}
  Suppose $\MM$ is a structure, $B \subseteq M$.
  Also fix a variable tuple $x$.
  \begin{itemize}
  \item \defn{A partial type over $B$} is a collection of formulas in variable $x$ with parameters from $B$.
  \item A partial type $p(x)$ has a \defn{realization} in $\MM$ if there exists $a \in M^{|x|}$ such that
    $\MM \models \phi(a)$ for all $\phi(x) \in p(x)$.
  \item A partial type is \defn{consistent} if its every finite subset of formulas has a realization.
  \item Suppose $a \in M^{|x|}$ and $\Delta \subseteq \LL(B)$ a collection of formulas in $x$.
    Define the \defn{$\Delta$-type of $a$ over $B$} to be a collection of formulas $\phi(x) \in \Delta$
    such that $\MM \models \phi(a)$.
    Denote it as $\tp_{\Delta}(a/B)$.
  \item Suppose $a \in M^{|x|}$.
    Define the \defn{type of $a$ over $B$} as the $\Delta$-type of $a$ over $B$ for $\Delta = \LL(B)$.
    Denote it as $\tp(a/B)$.
  \end{itemize}
\end{Definition}

Saturated structures is another important construction that we will be using.
Generally speaking, a lot of the model theory is done inside of saturated structures as it simplifies a lot of constructions.
The definition is as follows:
\begin{Definition}
  Let $\kappa$ be a cardinal.
  A structure $\MM$ is called $\kappa$-saturated if for all $B \subset M$ with $|B| < \kappa$
  we have that all consistent partial types over $B$ are realized in $\MM$.
\end{Definition}

Indiscernible sequences will be useful to us to describe dp-rank and dp-minimality.
They come up often in model theory as a way to leverage symmetry present in sequences and sets.
\begin{Definition}
  \begin{itemize}
  \item Suppose we have a sequence $(a_i)_{i \in \I}$ where $\I$ is an ordered index set.
    For $\J \subset \I$ the expression $a_{\J}$ denotes  a tuple obtained by concatenation of the sequence $(a_j)_{j \in \J}$
    (the sequence is ordered using the order of $\I$).    
  \item Suppose $\MM$ is a structure, $B \subseteq M$, and $\I$ is an oredred index set. 
    A sequence $(a_i)_{i \in \I}$ is called \defn{indiscernible over $B$} if
    for any two subsets $\J_1, \J_2 \subseteq \I$ of equal length we have 
    \begin{align*}
      \tp(a_{J_1}/B) = \tp(a_{J_2}/B).
    \end{align*}
  \item If we use the same definition, but allow tuples $a_{J_1}, a_{J_2}$ to be concatenated in arbitrary order,
    then we obtain the definition a sequence that is \defn{totally indiscernible over $B$} (alternatively a totally indiscernible set).
  \end{itemize}
\end{Definition}

Here is an important property of indiscernible sequences in stable thoeries:
\begin{Lemma}[see Lemma 9.1.1 in \cite{tent}] \label{totally}
  If a structure is stable then every indiscernible sequence is totally indiscernible.
\end{Lemma}

Sometimes instead of starting with an indiscernible sequence, we wish to construct one from a sequence with some degree of symmetry:
\begin{Lemma} [see Lemma 5.1.3 in \cite{tent}]
  Work in a $\aleph_1$-saturated structure $\MM$.
  Suppose $B \subset M$.
  Fix a variable tuple $x$ and a collection of formulas $\Delta(x_1, \ldots, x_n)$ with $|x_1| = |x|$.
  Suppose we can find an arbitrarily long sequence $(a_i)_{i \in \I}$ with $a_i \in M^{|x|}$ such that
  for any subset $\J \subseteq \I$ of length $n$ we have
  \begin{align*}
    \MM \models \Delta(a_{\J}).
  \end{align*}
  Then there exists an infinite indiscernible sequence $(a_i')_{i \in \omega}$ with
  \begin{align*}
    \MM \models \Delta(a_1', a_2', \ldots, a_n').
  \end{align*}
\end{Lemma}

Instead of working with types directly, it is often more convenient to work with automorphisms:
\begin{Definition}
  Suppose $\MM$ is a structure and $A \subset M$.
  An \defn{automorphism} of $\MM$ over $A$ is a bijection of $f \colon M \arr M$
  that fixes $A$ and preserves constants, relations, and functions of $\MM$.
  We use notation $f \in \Aut(\MM/A)$.
\end{Definition}

The following result is easy to show directly from the definition:
\begin{Lemma}
  Suppose $\MM$ is a structure, $A \subset M$, and $f \in \Aut(\MM/A)$.
  Suppose also that $a,b \in M^n$ such that $f(a) = b$.
  Then $tp(a/A) = tp(b/A)$.
\end{Lemma}

The converse of this result holds in a special type of structure:
\begin{Definition}
  Let $\MM$ be a structure and $\kappa$ a cardinal.
  Then $\MM$ is called \defn{strongly $\kappa$-homogeneous} if for all $A \subseteq M$ with $|A| < \kappa$
  we have that if for $a, b \in M^n$ if $tp(a/A) = tp(b/A)$ then
  there exists $f \in \Aut(\MM/A)$ such that $f(a) = b$.
\end{Definition}

Luckily, for a given theory one can always find a model sufficiently saturated and homogeneous:
\begin{Lemma} [see Theorem 6.1.7 in \cite{tent}]
  Let $T$ be a complete theory and $\kappa$ a cardinal.
  There exists a model of $T$ that is $\kappa$-saturated and strongly $\kappa$-homogeneous.
\end{Lemma}


\input{../../vc_intro}

Dp-rank is a common measure used in study of NIP theories, with dp-minimality being a special case.
Those notions originated in \cite{shelah_dp}, and further studied in \cite{dp_add}, showing, for example, that dp-rank is additive.
Here it is easiest for us to define dp-rank in terms of vc-density over indiscernible sequences.

\begin{Definition} \label{def_dp}
  \begin{itemize}
  \item
    Work in a $\aleph_1$-saturated first-order structure $M$.
    Fix a finite collection of formulas $\Phi(x, y)$ in the language of $M$.
    Suppose $A = (a_i)_{i \in \omega}$ is an indiscernible sequence with each $a_i \in M^{|x|}$.
    Let
    \begin{align*}
      \Ind(A, \Phi) = \{\phi(\bigcup_{i \in \N} a_i, b) \mid \phi \in \Phi, b \in M^{|y|}\} \subseteq \PP(M^{|x|}).     
    \end{align*}
    This gives rise to a set system $(M^{|x|}, \Ind(A, \Phi))$.
  \item Define
    \begin{align*}
      \vcind(\Phi) = \sup \curly{\vc(\Ind(A, \Phi)) \mid A = (a_i)_{i \in \N} \text{ is indiscernible}}.
    \end{align*}
  \item \defn{Dp-rank} of an $\aleph_1$-saturated structure $M$ is $\leq n$ if $\vcind(\phi) \leq n$ for all formulas $\phi$.
  \item \defn{Dp-rank} of a theory $T$ is $\leq n$ if dp-rank is $\leq n$ for any (all) $\aleph_1$-saturated model of $T$.
  \item A theory $T$ is said to have finite dp-rank if its dp-rank is $\leq n$ for some $n$.
  \item A theory $T$ is \defn{dp-minimal} if its dp-rank $\leq 1$.
  \end{itemize}
\end{Definition}

Refer to \cite{guingona} for the connection between to the classical definition of dp-rank and the definition given here.

There is a useful characterization of dp-minimality in terms of indiscernible sequences that will be useful for what we do:
\begin{Lemma} [see Lemma 1.4 in \cite{simon_dp_min}] \label{dp_min_simon}
  Suppose $\MM$ is an $\aleph_1$-saturated structure.
  Then the following are equivalent:
  \begin{itemize}
  \item $\MM$ is dp-minimal.
  \item For any countable indiscernible sequence $(a_i)_{i \in \I}$ indexed by a dense linear order $\I$,
    and any $c \in M$, there is $i_0$ in the completion of $I$
    such that the two sequences $\paren{\tp(a_i/c) \mid i < i_0}$ and
    $\paren{\tp(a_i/c) \mid i > i_0}$ are constant.
  \end{itemize}
\end{Lemma}
