\documentclass [PhD] {uclathes}
 
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{../../AMC_style}	
\usepackage{../../Research}
\usepackage{../../Thm}
\input {../../mymacros}                         % personal LaTeX macros
\newcommand{\chapa}{chapter }
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Usually things live in separate flies.
%
% \input {prelim}                           % preliminary page info

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%                          PRELIMINARY PAGES                           %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\title          {Computations of Vapnik-Chervonenkis Density \\
                in Various Model-Theoretic Structures}
\author         {Anton Bobkov} 
\department     {Mathematics}
% Note:  degreeyear should be optional, but as of  5-Feb-96
% it seems required or you get a year of ``2''.   -johnh
\degreeyear     {2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chair          {Matthias J.\ Aschenbrenner}
\member         {Vladimir V.\ Vassiliev}
\member         {Igor Pak} 
\member         {Yiannis N.\ Moschovakis}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\dedication     {\textsl{To my family and friends\\
                who have been unerringly supportive \\
                throughout my career path}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
  {I would like to start by thanking my advisor Matthias Aschenbrenner.
  This work would be impossible without his broad expertise, masterful guidance, insightful suggestions, and limitless patience.

  I am indebted to many people for their help throughout my career as a mathematician.
  Thank you to Erik Walsberg for the thorough and engaging discussions on a broad set of topics in model theory.
  A special thanks goes to Richard Elman whose incredible lectures were a deciding factor in my decision to study mathematics.
  I'd like to thank Henry Towsner, Yiannis Moschovakis, and Itay Neeman for introducing me to logic and showing that there is a deep and beautiful theory behind the formalism.
  Thank you to Andy Soffer and Scott Garrabrant for your help with combinatorics and graph theory.

  I wouldn't be where I am in life without my family.
  I would like to thank my parents Alexey and Rimma, and my brother Ilya for all their support and encouragement.

  Finally, I would like to thank Peter Lu and Alex Wright.
  Throughout the years of my graduate studies their companionship and friendship has been invaluable to me.

  Parts of this dissertation were supported financially by NSF Grant DMS-1044604 and 2016 Girsky Fellowship Award.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vitaitem{2011}{Sherwood Prize}
\vitaitem{\phantom{2011}}{\phantom{Sherwood Prize}}

\vitaitem{2011}{Departmental Highest Honors in Mathematics, College Honors}
\vitaitem{\phantom{2011}}{\phantom{Departmental Highest Honors in Mathematics, College Honors}}

\vitaitem{2011}{B.S.~(Mathematics) and B.A.~(Physics), UCLA, Los Angeles, California.}
\vitaitem{\phantom{2011}}{\phantom{B.S.~(Mathematics) and B.A.~(Physics), UCLA, Los Angeles, California.}}

\vitaitem{2016}{Excellence in Teaching Award}
\vitaitem{\phantom{2016}}{\phantom{Excellence in Teaching Award}}

\vitaitem{2016}{Girsky Fellowship Award}
\vitaitem{\phantom{2016}}{\phantom{Girsky Fellowship Award}} 

% \vitaitem   {1974--1975}
%                 {Campus computer center ``User Services'' programmer and
%                 consultant, Stanford Center for Information Processing,
%                 Stanford University, Stanford, California.}
% \vitaitem   {1974--1975}
%                 {Programmer, Housing Office, Stanford University.
%                 Designed a major software system for assigning
%                 students to on-campus housing.
%                 With some later improvements, it is still in use.}
% \vitaitem   {1975}
%                 {B.S.~(Mathematics) and A.B.~(Music),
%                 Stanford University.}
% \vitaitem   {1977}
%                 {M.A.~(Music), 
% \vitaitem   {1977--1979}
%                 {Teaching Assistant, Computer Science Department, UCLA.
%                 Taught sections of Engineering 10 (beginning computer
%                 programming course) under direction of Professor Leon
%                 Levine.
%                 During summer 1979, taught a beginning programming
%                 course as part of the Freshman Summer Program.}
% \vitaitem   {1979}
%                 {M.S.~(Computer Science), UCLA.}
% \vitaitem   {1979--1980}
%                 {Teaching Assistant, Computer Science Department, UCLA.}
% \vitaitem   {1980--1981}
%                 {Research Assistant, Computer Science Department, UCLA.}
% \vitaitem   {2007--2011}
%                 {Programmer/Analyst, Computer Science Department, UCLA.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \publication    {\textsl{MADHOUS Reference Manual.}
%                 Stanford University, Dean of Student Affairs
%                 (Residential Education Division), 1978.
%                 Technical documentation for the MADHOUS
%                 software system used to assign students to
%                 on-campus housing.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

            \abstract       {
  Aschenbrenner et al. have studied Vapnik-Chervonenkis density (VC-density) in the model-theoretic context.
  We investigate it further by computing it in some common structures: trees, Shelah-Spencer graphs, and an additive reduct
  of the field of $p$-adic numbers.
  In the theory of infinite trees we establish an optimal bound on the VC-density function.
  This generalizes a result of Simon showing that trees are dp-minimal. 
  In Shelah-Spencer graphs we provide an upper bound on a formula-by-formula basis and show that there isn't a uniform lower bound,
  forcing the VC-density function to be infinite.
  In addition we show that Shelah-Spencer graphs do not have a finite dp-rank,
  so they are not dp-minimal.
  There is a linear bound for the VC-density function in the field of $p$-adic numbers,
  but it is not known to be optimal.
  We investigate a certain $P$-minimal additive reduct of the field of $p$-adic numbers and
  use a cell decomposition result of Leenknegt to compute an optimal bound for that structure.
  Finally, following the results of Podewski and Ziegler we show that superflat graphs are dp-minimal.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\begin {document}
\makeintropages

\include{general_intro}
\include{Trees_vc_density}
\include{shelah_spencer}
\include{QP_reduct} 
\include{flat}
 

\bibliography {../../thesis_ref}    % bibliography references
\bibliographystyle {uclathes_my}
  
\end {document}