\documentclass [PhD] {uclathes}

\input{includes}

\title          {On bi-free probability and free entropy.}
\author         {Ian Lorne Charlesworth}
\department     {Mathematics}
% Note:  degreeyear should be optional, but as of  5-Feb-96
% it seems required or you get a year of ``2''.   -johnh
\degreeyear     {2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chair          {Dimitri~Y.~Shlyakhtenko}
\member         {Igor~Pak} %TODO: Igor is a non-certifying member. Should he still be included?
\member         {Sorin~Popa}
\member         {Milos~D.~Ercegovac}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\dedication     {...(todo: dedication goes here)...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments {...(todo: acknowledgements go here)...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vitaitem{2007-2012}{B.Math. Honours Pure Mathematics \& Honours Computer Science, University of Waterloo, Waterloo, Ontario, Canada.}
\vitaitem{2012-2016}{Natural Sciences and Engineering Research Council of Canada Postgraduate Scholarship.}
\vitaitem{2012-2017}{Ph.D. in Mathematics, University of California, Los Angeles, Los Angeles, California, U.S.A.}
\vitaitem{2016-2017}{U.C.L.A. Dissertation Year Fellowship.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\publication{ A. Nica, I. Charlesworth, and M. Panju. \emph{Analyzing Query Optimization Process: Portraits of Join Enumeration Algorithms}. IEEE 28th International Conference on Data Engineering (2012).}
\publication{ I. Charlesworth, B. Nelson, and P. Skoufranis. \emph{On Two-faced Families of Non-commutative Random Variables}, Canadian Journal of Mathematics \textbf{67} (2015), no. 6, 1290-1325.}
\publication{ I. Charlesworth, B. Nelson, and P. Skoufranis. \emph{Combinatorics of Bi-Freeness with Amalgamation}, Communications in Mathematical Physics \textbf{338} (2015), 801-847.}
\publication{ I. Charlesworth and D. Shlyakhtenko. \emph{Free Entropy Dimension and Regularity of Non-commutative Polynomials}, Journal of Functional Analysis \textbf{271} (2016), no. 8, 2274-2292.}
\publication{ I. Charlesworth. \emph{An alternating moment condition for bi-freeness}. arXiv preprint 1611.01262 (2016).}
\publication{ I. Charlesworth, K. Dykema, F. Sukochev, and D. Zanin. \emph{Joint spectral distributions and invariant subspaces for commuting operators in a finite von Neumann algebra}. arXiv preprint 1703.05695 (2017).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract{
	Free probability is a non-commutative analogue of probability theory.
	Recently, Voiculescu has introduced bi-free probability, a theory which aims to study simultaneously ``left'' and ``right'' non-commutative random variables, such as those arising from the left and right regular representations of a countable group.
	We introduce combinatorial techniques to characterise bi-free independence, generalising results of Nica and Speicher from the free setting to the bi-free setting.
	In particular, we develop the lattice of bi-non-crossing partitions which is deeply tied to the action of bi-freely independent random variables on a free product space.
	We use these techniques to show that a conjecture of Mastnak and Nica holds, and bi-free independence is equivalent to the vanishing of mixed bi-free cumulants vanishing.
	Moreover, we extend the theory into the operator-valued setting, introducing operator-valued cumulants which correspond to bi-freeness with amalgamation in the same way.
	Finally, we investigate regularity problems in algebras of non-commuting random variables.
	Using operator theoretic techniques show that in an algebra generated by non-commutative random variables which admit a dual system, any self-adjoint element with spectral measure singular with respect to Lebesgue measure is a multiple of $1$.
	We are also able to slightly improve on prior results in the literature and show that any non-constant self-adjoint polynomial evaluated at a set of non-commutative random variables which are free, algebraic, and have finite free entropy must produce a variable with finite free entropy.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin {document}
\makeintropages

\input{introduction}

\input{bifreeequiv}

\input{amalgamatedbifree}

\input{entropy}
 
\bibliography {/Users/ilc/Documents/Papers/biblio}
\bibliographystyle {thesis}

\end {document}

