\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{graphicx}%
\usepackage{fancyhdr}


\theoremstyle{plain} \numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{finalremark}[theorem]{Final Remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}{Question} \topmargin-2cm

\textwidth6in
%\textheight23cm
%\oddsidemargin0.5in
%\evensidemargin0.5in
\setlength{\topmargin}{0in}
\addtolength{\topmargin}{-\headheight}
\addtolength{\topmargin}{-\headsep}
%\setlength{\textheight}{8.6in}
\setlength{\oddsidemargin}{0in}
%\setlength{\textwidth}{6.5in}
\oddsidemargin  0.0in \evensidemargin 0.0in \parindent0em

\pagestyle{fancy}\lhead{Teaching history} \rhead{September 2015}
\chead{{\large{\bf Jaclyn Lang}}} \lfoot{} \rfoot{\bf \thepage} \cfoot{}

\newcounter{list}


\begin{document}

%\raisebox{1cm}

{\large\textbf{Teaching History - UCLA}} \medskip

\begin{itemize} 
\item Won departmental teaching award - May 2014
\item Teaching assistant for MATH 61: Discrete Mathematics (Spring 2014)
\item Teaching assistant for MATH 110B: Algebra - Group Theory (Winter 2014) 
\item Teaching assistant for MATH 495: Teaching College Mathematics (Fall 2013)
\item Teaching assistant for Math 31B: Integration \& Infinite Series (Fall 2013, Summer 2013, Spring 2011)
\end{itemize} \medskip

{\large\textbf{Teaching History - outside UCLA}} \medskip

\begin{itemize} 
\item Teaching assistant for Summer Program for Women in Mathematics (SPWM), George Washington University (Summer 2012)
	\begin{itemize}
	\item And then there were four: normed division algebras, taught by Alissa Crans (Loyola Marymount University)
	\item Semigroups, taught by Berit Givens (California State University, Pomona)
	\end{itemize} 
\item Counselor for Program in Mathematics for Young Scientists (PROMYS), Boston University (Summer 2010)
\item Problem Session Holder at Bryn Mawr College for the following courses
	\begin{itemize}
	\item Abstract Algebra II (Spring 2009)
	\item Abstract Algebra I (Fall 2008)
	\item Transitions to Higher Mathematics (Spring 2007)
	\item Calculus 101 (Fall 2006)
	\end{itemize}
\item Peer Instructor for Bryn Mawr College for the following courses
	\begin{itemize}
	\item Linear Algebra (Spring 2008)
	\item Multivariable Calculus (Fall 2007)
	\end{itemize}
\item Grader at Bryn Mawr College for the following courses
	\begin{itemize}
	\item Multivariable calculus (Fall 2007)
	\item Transitions to Higher Mathematics (Spring 2007)
	\item Multivariable Calculus (enriched) (Fall 2006)
	\end{itemize}
\item Private mathematics tutor (2008-2009)
\end{itemize}

\medskip

{\large\textbf{Educational Outreach}} \medskip

\begin{itemize} 
\item Presenter at EmpowHer STEM Day, ``The Monty Hall Problem", (May 2014, 2015)
\item Talk at high school section of LA Math Circle, ``Absolute values and $p$-adic numbers" (April 2012)
\end{itemize}

\medskip

{\large{\textbf{Sample teaching evaluations - UCLA}}
 \begin{description}

    \item[\normalsize{General Comments}] 
    	\begin{itemize}
		\item I was unable to attend discussion, however I am basing this review off the review session the TA hosted.  She provided very valuable insight into the subject and expanded very well upon course ideas, showing more ways to approach problems that were introduced in lecture.  (MATH 61)
		\item Jackie was a great TA.  She knew the course material very well and was able to explain all of the material in clear ways.  She always tried to answer all questions and if wasn't able to answer the question during discussion or office hours would make sure to send out an email.  I am very happy I had her as a TA for this course. (MATH 31B, Fall 2013)
		\item My TA did an exceptional job, both in her discussion section and also in office hours.  When the professor didn't go over certain aspects clearly in class, she was able to explain things thoroughly.  She was also very supportive of all of her students and was happy to help answer our questions.  I didn't find it hard at all to ask for help.  (MATH 31B, Fall 2013)
		\item Compared to a previous TA I had for math, Jackie was an excellent TA.  She was knowledgable about what she was teaching and was always prepared.  She taught us so that our weekly quizzes seemed like they were easy, so we didn't have to stress as much on grades as much as actually learning the material.  She encourages student participation and students interacting actively with each other.  (MATH 31B, Fall 2013)
		\item Jackie was very helpful in making sure we understood the material, and very accommodating during office hours.  Even while strapped for time, she would endeavor to answer as many questions as possible in as clear a manner as she could.  Her quizzes also ensured at least our familiarity with the material.  I find nothing wrong with her teaching.  (MATH 31B,  Fall 2013)
		\item Jackie was an excellent TA for this course.  She gave us lots of useful advice and helped facilitate great discussions.  (MATH 495)
		\item Jacky is an amazing TA.  She takes time to ensure everyone understands the concepts and is always prepared to meet up out of class time to discuss any problems.  She should be the one teaching the class.  Also I love the fact that i can actually understand her and she is not socially awkward like a lot of the other math TA's.  GREAT TA (MATH 31B, Summer 2013)
	\end{itemize}

    \item[\normalsize{Communication Skills}]  
    	\begin{itemize}
		\item Wonderful TA.  Great communicator and always clearly and directly answered all questions.  I often found myself learning much more from the once a week 50 minute discussion than from an entire week of lecture.  I wish that she had been giving the class lectures. (MATH 61)
		\item In section, Jackie really tried to clarify the concepts the professor hastily, and sometimes sloppily, covered.  She explains herself very well.  She's a great TA for the class.  (MATH 31B, Fall 2013)
		\item She is a great TA that knows the material very well.  Whenever students brought up questions during discussion, she would be able to answer the questions in multiple ways so that we could all understand where the answers came from.  The only bad thing was her availability, which was rather limited.  But when I went to office hours and discussion, I thought I learned a fair amount of material.  (MATH 31B, Fall 2013)
		\item Jackie is a godsend!  When I stumbled into section, mind twisted and notes (taken verbatim from what the professor wrote on the board) incomprehensible, Jackie broke down what the professor took 2 hours to cover clumsily into 50 minutes of easy theorems and steps.  If only Jackie taught the class, I might feel like spending my summer here was worth it.  She's super available, helpful, and a fantastic teacher.  (MATH 31B, Summer 2013)
		\item Jaclyn is a clear and concise TA that makes learning the most annoyingly tedious methods of math a quick abc checklist that every student now possesses.  Wished she was actually the professor.  (MATH 31B, Summer 2013)
		\item If it were not for Jaclyn, I, along with many others in the class, would not have been able to understand the material.  She comes to discussion with a very structured lesson plan that helps us understand exactly what she is trying to convey.  The professor does a really poor job in conveying knowledge to us, and he often skips steps and assumes we understand.  Jaclyn's lesson plans really break it down for us, and without her, I would not be doing nearly as well in this class as I am right now.  She is always very approachable after discussions and wants you to understand exactly what you are doing wrong.  She is also very open during office hours and helps us go step by step and understand the intuition behind the math we are doing.  She is one of the best TAs I've had thus far at UCLA and I am a third year.  (MATH 31B, Summer 2013)
		\item I was able to understand Jaclyn and everything she says.  She's organized and I believe that's a very important factor.  She also holds review sessions before midterms and they were extremely helpful, too.  Sometimes, Jaclyn seems unsure of what she's doing.  I guess because it's her first time teaching, but towards the end of the quarter, it was better.  She's a great TA.  (MATH 31B, Spring 2011)
		\item Jaclyn is very helpful since I could never make her OH she is always willing to stay after class for a bit to help me on my questions.  During class she'd made the atmosphere comfortable enough that I wouldn't be second to ask her questions.  (MATH 31B, Spring 2011)
		\item Jaclyn Lang is a very helpful TA who is always available and willing to help inside and outside of classroom.  She is also very knowledgable, organized and prepared.  She is a great TA.  (MATH 31B, Spring 2011)
		\item Jackie did a wonderful job of helping us understand the material.  She used great example problems.  She has been the best TA I have had at UCLA.  (MATH 31B, Spring 2011)
		\item Jaclyn is an exceptional TA.  She is always available to answer questions.  Her discussions are always very organized and she takes time to prepare sessions despite her own very busy schedule.  She actually wasn't my ``assigned" TA but my own TA did not prepare discussions so I chose to attend her sections.  I don't know how I would have done it without her because the professor isn't very good at teaching either.  (MATH 31B, Spring 2011)
	\end{itemize}

    \item[\normalsize{Style of Discussion Section}] 
    	\begin{itemize}
		\item Lang is a very efficient teaching assistant.  She would go through every homework problems we had encountered, which helped us to learn the materials a lot.  It would be better if Lang could provide some extra lecture notes although that's optional.  Anyway, I believe that Lan would be a great instructor in the future.  Really thank you for all your efforts! (MATH 61)
		\item Great TA, very very helpful and explained concepts clearly.  I like the structure of discussion where she covers some of the concepts but focuses on examples relevant to the concepts we learned previously.  And overall, she was very enthusiastic and prepared to teach! (MATH 110B)
		\item Jackie is a great TA.  She is very passionate about the students learning the material correctly.  Although she is a bit harsh on grading homework assignments, she was very fair and wrote many helpful comments on every homework assignment.  She also brought in visual aids to help us better visualize $3$-dimensional shapes.  I found the discussion sections very helpful. (MATH 110B)
		\item organized lectures, with plenty of time to answer any questions on homework or from lecture and managed to provide extremely simple yet accurate definitions of the group structures to allow us to grasp them properly. on top of all that, the level of patience for the lack of student participation while working through proofs in class was amazing to say the least. (MATH 110B)
		\item Discussion sessions are so helpful because my TA was very clear and effective in teaching the information.  However, I feel like discussions were way too short for going over the material because the quiz takes 10 minutes and we only have 40 or less minutes to go over the material.  most of the time, we are only able to go over 3 homework problems when we need help on 7 or more problems. (MATH 31B, Fall 2013)
		\item Jackie was a wonderful TA!  Her effective and straightforward teaching enhanced my learning and made me enjoy the subject.  The structure of sections (short period of group work then examples on the board) utilized the 50 min well.  Furthermore, her kindness and encouragement decreased my stress and made me want to go to section every week.  She thoroughly answered all questions and was very good at explaining concepts in terms students were able to understand.  I hope all my future TA's are as great as Jackie. (MATH 31B, Fall 2013)
		\item My TA shows a lot of concern for whether we understand the material or not.  She takes the time to go over concepts more than once.  She's organized in preparing her notes before discussion.  She even took extra time out of discussion to hold review sessions for our exams.  Her effectiveness as a TA is excellent.  Though she has trouble explaining things in a way that we will understand, she keeps trying until we do understand the material.  I'm glad Jackie was a TA for this class.  (MATH 31B, Summer 2013)
	\end{itemize}
     \item[\normalsize{Office Hours}]
     	\begin{itemize}
		\item She's really nice and approachable, and her office hour is very organized.. everytime I go to her office hours, I feel like I learned more than I could learn in the class or discussion session.  Especially, Abstract Algebra class requires you to organize your thought and write neat proof..and she was perfectly helpful to organize my though..so that I could write neat proof on my own.  In this regard, she is really effective TA, especially for Algebra class.  (MATH 110B)
	\end{itemize}
    
\end{description}

{\large{\textbf{Sample teaching evaluations - SPWM}}
 \begin{itemize}
\item Jackie was completely fantastic.  She answered all of my questions and was always giving advice.  She is very smart and always approachable.  She was one of the most helpful parts of the program.
\item The teaching assistants were excellent.  They were with us through the end and reassuring us when things got hard.  They were definitely available when ever we needed them.
\item (Other TA) and Jackie were both very nice.  They made sure to be available whenever we needed them and gave us very good feedback for presentations.  It was also nice to hear their thoughts on grad school.
\item Both of our TAs were awesome!  They were very willing to help us practice our projects, and talk to us about math outside of classes.  For example, both TAs talked w/me about algebraic topology, and I appreciated this.
\end{itemize}

\end{document}