\documentclass{report}

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{../AMC_style}	
\usepackage{../Research}
\usepackage{../Thm}

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}


\usepackage{enumitem}  
\usepackage{mathrsfs} 
\usepackage{pgfpages}
\usepackage{setspace} 

\doublespacing
%\usepackage[margin=.75in]{geometry}
%\pgfpagesuselayout{2 on 1}

\newcommand{\X}{\mathcal X}
\newcommand{\Y}{\mathcal Y}


\DeclareMathOperator{\TT}{\mathcal T}
\DeclareMathOperator{\PR}{P}
\DeclareMathOperator{\cl}{cl}
\newcommand{\CS}{\mathcal S}

\DeclareMathOperator{\cx}{Complexity}
\newcommand{\K}{\boldface K_\alpha}
\renewcommand{\S}{S_\alpha}

\DeclareMathOperator{\I}{\mathcal I}
\DeclareMathOperator{\J}{\mathcal J}
\DeclareMathOperator{\acl}{acl}

\renewcommand{\AA}{\mathscr A}
\newcommand{\BB}{\mathscr B}
\newcommand{\DD}{\mathscr D}
\newcommand{\II}{\mathscr I}
\newcommand{\MM}{\mathscr M}

\newcommand{\A}{\mathcal A}
\newcommand{\B}{\mathcal B} 
\renewcommand{\C}{\mathcal C}
\newcommand{\D}{\mathcal D}
\newcommand{\F}{\mathcal F}
\newcommand{\G}{\mathcal G}
\renewcommand{\H}{\mathcal H}
\renewcommand{\LL}{\mathcal L}
\newcommand{\LLA}{\mathcal L_{aff}}
\newcommand{\LLM}{\mathcal L_{Mac}}
\newcommand{\M}{\mathcal M}

\newcommand{\U}{\mathcal U}	

\DeclareMathOperator{\Sg}{Sg}
\DeclareMathOperator{\It}{Tp}
\DeclareMathOperator{\Sub}{Sub}
\DeclareMathOperator{\Ct}{Ct}
\DeclareMathOperator{\vecspan}{span}
\DeclareMathOperator{\val}{val}
\DeclareMathOperator{\vval}{val}
\DeclareMathOperator{\tval}{T-val}
\DeclareMathOperator{\tfl}{T-fl}
\DeclareMathOperator{\inti}{I}

\newcommand{\defn}{\underline}
\newcommand{\interval}{\inti(t, \alpha_L, \alpha_U)}

\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\paren}[1]{\left(#1\right)}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\agl}[1]{\left\langle #1 \right\rangle}

\providecommand{\floor}[1]{\left \lfloor #1 \right \rfloor }


\begin{document}
%\input{../vc_intro.tex}

 
\tableofcontents{}

\chapter{Inroduction}

\input{../vc_intro}

\chapter{vc-density for trees}

\input{Trees_vc_density}
 
\chapter{vc-density in an additive reduct of the $P$-adic numbers}

\input{QP_reduct}

\chapter{shelah-spencer graphs}

\input{shelah_spencer}

\chapter{Flat graphs}

\input{flat}

\begin{thebibliography}{9}

  
\bibitem{laskowski}
  Michael C. Laskowski, \textit{A simpler axiomatization of the Shelah-Spencer almost sure theories},
  Israel J. Math. \textbf{161} (2007), 157–186. MR MR2350161	
\bibitem{density}
  M. Aschenbrenner, A. Dolich, D. Haskell, D. Macpherson, S. Starchenko,
  \textit{Vapnik-Chervonenkis density in some theories without the independence property}, I,
  Trans. Amer. Math. Soc. 368 (2016), 5889-5949
\bibitem{reduct}
  E. Leenknegt. \textit{Reducts of $p$-adically closed fields}, Archive for Mathematical Logic, 53(3):285-306, 2014
\bibitem{ash7}
  P. Assouad, \textit{Densit´e et dimension}, Ann. Inst. Fourier (Grenoble) 33 (1983), no. 3, 233–282.
\bibitem{ash8}
  P. Assouad, \textit{Observations sur les classes de Vapnik-Cervonenkis et la dimension combinatoire de Blei},
  in: Seminaire d’Analyse Harmonique, 1983–1984, pp. 92–112, Publications Math´ematiques
  d’Orsay, vol. 85-2, Universit´e de Paris-Sud, D´epartement de Math´ematiques, Orsay, 1985.
\bibitem{sauer}
  N. Sauer, \textit{On the density of families of sets}, J. Combinatorial Theory Ser. A 13 (1972), 145–147.
\bibitem{shelah}
  S. Shelah, \textit{A combinatorial problem; stability and order for models and theories in infinitary languages},
  Pacific J. Math. 41 (1972), 247–261.
\bibitem{simon_dp_min}
  P. Simon,
  \textit{On dp-minimal ordered structures},
  J. Symbolic Logic 76 (2011), no. 2, 448-460
\bibitem{parigot_trees}
  Michel Parigot.
  Th\'eories d'arbres.
  \textit{Journal of Symbolic Logic}, 47, 1982, 841-853
\bibitem{stable_graphs}
	Klaus-Peter Podewski and Martin Ziegler. Stable graphs. \textit{Fund. Math.}, 100:101-107, 1978.
\bibitem{infinite_megner}
	Aharoni, Ron and Berger, Eli (2009). "Menger's Theorem for infinite graphs". \textit{Inventiones Mathematicae} 176: 1–62

\end{thebibliography}

\end{document}